---
title: "Data checks"
author: "Jill Guerra"
date: "January 3, 2016"
output: 
  html_document:
    keep_md: true 
---

###Load packages 
```{r}
library(ggplot2)
library(car) 
suppressPackageStartupMessages(library(dplyr))
library(gridExtra) # for grid.arrange 
library("reshape2")
#install.packages("png")
library("png")
#install.packages("raster")
library("raster") # for arranging pngs 
#install.packages("moments")
library("moments") # for skew & kurtosis
library(knitr)
```

###Import file
```{r}
fulldf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_01.06.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
```

###Reshape data 
```{r, echo=FALSE}
# # this may be useful down the road but not using at the moment. 
# aei_melted <- melt(fulldf_aei) # new dataframe with melted data 
# aes_index_var <- c("nochem", "croprot", "covercrop", "apm", "noconvtill", "directplanting", "lowtill", "drip") # drop of just index variables 
# aes_socecon_var <- c("lowincome", "offfarminc", "association", "credit", "regtech", "famlab")# group of just the social and economic variables 
# 
# ####### WORKING ON THIS 
# aei_meltedtest <- melth(fulldf_aei, id.var)
# test <- c("nochem", "croprot", "covercrop")
# aei_melted2 <- aei_melted %>% 
#   filter(variable %in% test) # new dataframe with just the index variables 
# 
# (ggplot(aei_melted2, aes(X, y = value, colour = variable)) + 
#   geom_point() +
#   geom_smooth()) # graph works. But now I really know that this graph should be showing the fitted values not the points. 
# 
# # want to use this! 
# (ggplot(aei_melted, aes(x=lifeExp, fill=region)) +
#    geom_density(binwidth=.5, alpha=.5, position="identity") +
#   coord_flip() + 
#   facet_grid(. ~ year) +
#   ggtitle("Density of life expectancy by year in the Americas") +
#   theme(axis.ticks = element_blank(), axis.text.x = element_blank()))  
# 
# # not sure how to use this because the x variable doesn't make sense 

```

###Checking distribution 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# loop to look at the distributions for all variables. It currently works. Saves all individual graphs in png files 
# nm <- names(fulldf_aei[,3:18]) # calls all the AEI variables 
# for (i in seq_along(nm)) {
#   plots <- ggplot(fulldf_aei, aes_string(x=nm[i])) +
#     geom_histogram()
#   ggsave(plots,filename=paste("dist",nm[i],".png",sep=""))
#  
# }

# rl = lapply(sprintf("dist",i,".png",sep=""), png::readPNG)
# gl = lapply(rl, grid::rasterGrob)
# do.call(gridExtra::grid.arrange, gl) 

#histograms
a <- ggplot(fulldf_aei, aes(x = nochem)) +
 geom_histogram()
b <- ggplot(fulldf_aei, aes(x = usefert)) +
 geom_histogram()
c <- ggplot(fulldf_aei, aes(x = orgcomp)) +
 geom_histogram()
d <- ggplot(fulldf_aei, aes(x = manure)) +
 geom_histogram()
e <- ggplot(fulldf_aei, aes(x = nitchem)) +
 geom_histogram()
f <- ggplot(fulldf_aei, aes(x = notnitchem)) +
 geom_histogram()
g <- ggplot(fulldf_aei, aes(x = covercrop)) +
 geom_histogram()
h <- ggplot(fulldf_aei, aes(x = Innoculents)) +
 geom_histogram()
i <- ggplot(fulldf_aei, aes(x = croprot)) +
 geom_histogram()
j <- ggplot(fulldf_aei, aes(x = noconvtill)) +
 geom_histogram()
k <- ggplot(fulldf_aei, aes(x = directplanting)) +
 geom_histogram()
l <- ggplot(fulldf_aei, aes(x = lowtill)) +
 geom_histogram()
m <- ggplot(fulldf_aei, aes(x = soil)) +
 geom_histogram()
n <- ggplot(fulldf_aei, aes(x = drip)) +
 geom_histogram()
o <- ggplot(fulldf_aei, aes(x = apm)) +
 geom_histogram()
p <- ggplot(fulldf_aei, aes(x = famlab)) +
 geom_histogram()
q <- ggplot(fulldf_aei, aes(x = associated)) +
 geom_histogram()
r <- ggplot(fulldf_aei, aes(x = lowincome)) +
 geom_histogram()
s <- ggplot(fulldf_aei, aes(x = regtech)) +
 geom_histogram()
t <- ggplot(fulldf_aei, aes(x = credit)) +
 geom_histogram()
u <- ggplot(fulldf_aei, aes(x = offfarminc)) +
 geom_histogram()

grid.arrange(a,b,c,d,e,f,g,h,i,j,k,l,m,n,o,p,q,r,s,t,u, ncol=3)

##### Look again at binwidth at some point. Note

```

####Results: 


###DATA CHECKING 
```{r, results="hide"}
# create dataframe without the first two columns because they aren't numbers 
df_onlynum <- fulldf_aei[,3:(ncol(fulldf_aei))] # drop the first two columns 

#skewness 
skew <- apply(df_onlynum, 2, skewness, na.rm=TRUE) # call correct df, 2 means looking at columns (1 would indicate looking rows), skewness is the function applied, ignore NAs 

#kurtosis
kurt <- apply(df_onlynum, 2, kurtosis, na.rm=TRUE) # df, looking at columns, kurtosis is function, ignore NAs

#variance 
variance <- apply(df_onlynum, 2, var, na.rm=TRUE)# df, looking at columns, variance is function, ignore NAs

#standard deviations 
sd <- apply(df_onlynum, 2, sd, na.rm=TRUE)


# coefficient of variation 
# CV <- function(mean, sd) {
#   (sd/mean)*100
# }


```


###Create table with values for data checks
```{r, }
#combine values lists into a dataframe 
data_checks <- cbind(kurt, skew, variance, sd) 
knitr::kable(data_checks) # nice table with all the data 

```

###Checking Bivariate relationships of index components 
```{r, echo=FALSE, warning=FALSE}
# NOCHEM
a1 <- ggplot(fulldf_aei, aes(nochem, croprot)) +
  geom_point()+
  stat_smooth() 
a2 <- ggplot(fulldf_aei, aes(nochem, covercrop)) +
  geom_point() +
  stat_smooth() 
a3 <- ggplot(fulldf_aei, aes(nochem, apm)) +
  geom_point() +
  stat_smooth() 
a4 <- ggplot(fulldf_aei, aes(nochem, noconvtill)) +
  geom_point() +
  stat_smooth() 
a5 <- ggplot(fulldf_aei, aes(nochem, directplanting)) +
  geom_point() +
  stat_smooth() 
a6 <- ggplot(fulldf_aei, aes(nochem, lowtill)) +
  geom_point() +
  stat_smooth() 
a7 <- ggplot(fulldf_aei, aes(nochem, soil)) +
  geom_point() +
  stat_smooth() 
a8 <- ggplot(fulldf_aei, aes(nochem, drip)) +
  geom_point() +
  stat_smooth()
a9 <- ggplot(fulldf_aei, aes(nochem, usefert)) +
  geom_point() +
  stat_smooth()
a10 <- ggplot(fulldf_aei, aes(nochem, orgcomp)) +
  geom_point() +
  stat_smooth()
a11 <- ggplot(fulldf_aei, aes(nochem, manure)) +
  geom_point() +
  stat_smooth()
grid.arrange(a1,a2,a3,a4,a5,a6,a7,a8,a9,a10,a11, ncol=3)


# CROPROT
b1 <- ggplot(fulldf_aei, aes(croprot, covercrop)) +
  geom_point() +
  stat_smooth() 
b2 <- ggplot(fulldf_aei, aes(croprot, apm)) +
  geom_point() +
  stat_smooth() 
b3 <- ggplot(fulldf_aei, aes(croprot, noconvtill)) +
  geom_point() +
  stat_smooth() 
b4 <- ggplot(fulldf_aei, aes(croprot, directplanting)) +
  geom_point() +
  stat_smooth() 
b5 <- ggplot(fulldf_aei, aes(croprot, lowtill)) +
  geom_point() +
  stat_smooth()
b6 <- ggplot(fulldf_aei, aes(croprot, soil)) +
  geom_point() +
  stat_smooth()
b7 <- ggplot(fulldf_aei, aes(croprot, drip)) +
  geom_point() +
  stat_smooth()
b8 <- ggplot(fulldf_aei, aes(croprot, usefert)) +
  geom_point() +
  stat_smooth()
b9 <- ggplot(fulldf_aei, aes(croprot, orgcomp)) +
  geom_point() +
  stat_smooth()
b10 <- ggplot(fulldf_aei, aes(croprot, manure)) +
  geom_point() +
  stat_smooth()
grid.arrange(b1,b2,b3,b4,b5,b6,b7,b8, b9,b10, ncol=3) # put all the graphs into one grid 

# COVERCROP
c1 <- ggplot(fulldf_aei, aes(covercrop, apm)) +
  geom_point() +
  stat_smooth() 
c2 <- ggplot(fulldf_aei, aes(covercrop, noconvtill)) +
  geom_point() +
  stat_smooth() 
c3 <- ggplot(fulldf_aei, aes(covercrop, directplanting)) +
  geom_point() +
  stat_smooth() 
c4 <- ggplot(fulldf_aei, aes(covercrop, lowtill)) +
  geom_point() +
  stat_smooth()
c5 <- ggplot(fulldf_aei, aes(covercrop, soil)) +
  geom_point() +
  stat_smooth()
c6 <- ggplot(fulldf_aei, aes(covercrop, drip)) +
  geom_point() +
  stat_smooth()
c7 <- ggplot(fulldf_aei, aes(covercrop, usefert)) +
  geom_point() +
  stat_smooth()
c8 <- ggplot(fulldf_aei, aes(covercrop, orgcomp)) +
  geom_point() +
  stat_smooth()
c9 <- ggplot(fulldf_aei, aes(covercrop, manure)) +
  geom_point() +
  stat_smooth()
grid.arrange(c1,c2,c3,c4,c5,c6,c7,c8,c9, ncol=3) # put all the graphs into one grid 

# APM 
d1 <- ggplot(fulldf_aei, aes(apm, noconvtill)) +
  geom_point() +
  stat_smooth() 
d2 <- ggplot(fulldf_aei, aes(apm, directplanting)) +
  geom_point() +
  stat_smooth() 
d3 <- ggplot(fulldf_aei, aes(apm, lowtill)) +
  geom_point() +
  stat_smooth()
d4 <- ggplot(fulldf_aei, aes(apm, soil)) +
  geom_point() +
  stat_smooth()
d5 <- ggplot(fulldf_aei, aes(apm, drip)) +
  geom_point() +
  stat_smooth()
d6 <- ggplot(fulldf_aei, aes(apm, usefert)) +
  geom_point() +
  stat_smooth()
d7 <- ggplot(fulldf_aei, aes(apm, orgcomp)) +
  geom_point() +
  stat_smooth()
d8 <- ggplot(fulldf_aei, aes(apm, manure)) +
  geom_point() +
  stat_smooth()
grid.arrange(d1,d2,d3,d4,d5,d6,d7,d8, ncol=3) # put all the graphs into one grid 


#DRIP
e1 <- ggplot(fulldf_aei, aes(drip, noconvtill)) +
  geom_point() +
  stat_smooth() 
e2 <- ggplot(fulldf_aei, aes(drip, directplanting)) +
  geom_point() +
  stat_smooth() 
e3 <- ggplot(fulldf_aei, aes(drip, lowtill)) +
  geom_point() +
  stat_smooth()
e4 <- ggplot(fulldf_aei, aes(drip, soil)) +
  geom_point() +
  stat_smooth()
e5 <- ggplot(fulldf_aei, aes(drip, usefert)) +
  geom_point() +
  stat_smooth()
e6 <- ggplot(fulldf_aei, aes(nochem, orgcomp)) +
  geom_point() +
  stat_smooth()
e7 <- ggplot(fulldf_aei, aes(nochem, manure)) +
  geom_point() +
  stat_smooth()
grid.arrange(e1,e2,e3,e4,e5, ncol=3)

#LOWTILL
f1 <- ggplot(fulldf_aei, aes(lowtill, noconvtill)) +
  geom_point() +
  stat_smooth() 
f2 <- ggplot(fulldf_aei, aes(lowtill, directplanting)) +
  geom_point() +
  stat_smooth() 
f3 <- ggplot(fulldf_aei, aes(lowtill, soil)) +
  geom_point() +
  stat_smooth()
f4 <- ggplot(fulldf_aei, aes(lowtill, usefert)) +
  geom_point() +
  stat_smooth()
grid.arrange(f1,f2,f3,f4, ncol=3)

```


####Results: 

- very clear relatioship between nochem and fertilizer use (likely because most fertilizer use is chemical). 
- some relationship  between fert and covercrop/croprot/apm


###Checking bivariate relationships of SOCECON variables 
```{r, echo=FALSE, warning=FALSE}
# CREDIT
z <- ggplot(fulldf_aei, aes(credit, associated)) +
  geom_point() +
  stat_smooth() 
z1 <- ggplot(fulldf_aei, aes(credit, famlab)) +
  geom_point() +
  stat_smooth()
z2 <- ggplot(fulldf_aei, aes(credit, lowincome)) +
  geom_point() +
  stat_smooth() 
z3 <- ggplot(fulldf_aei, aes(credit, offfarminc)) +
  geom_point() +
  stat_smooth() 

grid.arrange(z, z1, z2,z3, ncol=3)

# ASSOCIATED
y <- ggplot(fulldf_aei, aes(associated, famlab)) +
  geom_point() +
  stat_smooth()
y1 <- ggplot(fulldf_aei, aes(associated, lowincome)) +
  geom_point() +
  stat_smooth() 
y2 <- ggplot(fulldf_aei, aes(associated, offfarminc)) +
  geom_point() +
  stat_smooth() 

grid.arrange(y, y1, y2, ncol=3)

# FAMLAB
x <- ggplot(fulldf_aei, aes(famlab, lowincome)) +
  geom_point() +
  stat_smooth() 
x1 <- ggplot(fulldf_aei, aes(famlab, offfarminc)) +
  geom_point() +
  stat_smooth() 
grid.arrange(x, x1, ncol=2)

# lowincome & offfarm
(w <- ggplot(fulldf_aei, aes(lowincome, offfarminc)) +
  geom_point() +
  stat_smooth()) 
```

####Results

- credit and associated positively related 
- no other ones are related in any significant way. 

###Relationship between nochem and SOCECON variables 
```{r, echo=FALSE, warning=FALSE}
#NOCHEM & SE VARIABLES
n <- ggplot(fulldf_aei, aes(nochem, associated)) +
  geom_point() +
  stat_smooth() 
n1 <- ggplot(fulldf_aei, aes(nochem, famlab)) +
  geom_point() +
  stat_smooth()
n2 <- ggplot(fulldf_aei, aes(nochem, lowincome)) +
  geom_point() +
  stat_smooth() 
n3 <- ggplot(fulldf_aei, aes(nochem, offfarminc)) +
  geom_point() +
  stat_smooth() 
n4 <- ggplot(fulldf_aei, aes(nochem, credit)) +
  geom_point() +
  stat_smooth() 
grid.arrange(n, n1, n2,n3,n4, ncol=3)

```

```{r}

t1 <- ggplot(fulldf_aei, aes(associated, nochem)) +
  geom_point() +
  stat_smooth() 
t2 <- ggplot(fulldf_aei, aes(associated, usefert)) +
  geom_point() +
  stat_smooth() 
t3 <- ggplot(fulldf_aei, aes(associated, nitchem)) +
  geom_point() +
  stat_smooth() 
t4 <- ggplot(fulldf_aei, aes(associated, notnitchem)) +
  geom_point() +
  stat_smooth() 
t5 <- ggplot(fulldf_aei, aes(associated, orgcomp)) +
  geom_point() +
  stat_smooth() 
t6 <- ggplot(fulldf_aei, aes(associated, manure)) +
  geom_point() +
  stat_smooth() 
t7 <- ggplot(fulldf_aei, aes(associated, covercrop)) +
  geom_point() +
  stat_smooth() 
t8 <- ggplot(fulldf_aei, aes(associated, croprot)) +
  geom_point() +
  stat_smooth() 
t9 <- ggplot(fulldf_aei, aes(associated, lowtill)) +
  geom_point() +
  stat_smooth() 
t10 <- ggplot(fulldf_aei, aes(associated, soil)) +
  geom_point() +
  stat_smooth() 
t11 <- ggplot(fulldf_aei, aes(associated, drip)) +
  geom_point() +
  stat_smooth() 
grid.arrange(t1,t2,t3,t4,t5,t6,t7,t8,t9,t10,t11, ncol=3)

```

```{r}
u1 <- ggplot(fulldf_aei, aes(famlab, nochem)) +
  geom_point() +
  stat_smooth() 
u2 <- ggplot(fulldf_aei, aes(famlab, usefert)) +
  geom_point() +
  stat_smooth() 
u3 <- ggplot(fulldf_aei, aes(famlab, nitchem)) +
  geom_point() +
  stat_smooth() 
u4 <- ggplot(fulldf_aei, aes(famlab, notnitchem)) +
  geom_point() +
  stat_smooth() 
u5 <- ggplot(fulldf_aei, aes(famlab, orgcomp)) +
  geom_point() +
  stat_smooth() 
u6 <- ggplot(fulldf_aei, aes(famlab, manure)) +
  geom_point() +
  stat_smooth() 
u7 <- ggplot(fulldf_aei, aes(famlab, covercrop)) +
  geom_point() +
  stat_smooth() 
u8 <- ggplot(fulldf_aei, aes(famlab, croprot)) +
  geom_point() +
  stat_smooth() 
u9 <- ggplot(fulldf_aei, aes(famlab, lowtill)) +
  geom_point() +
  stat_smooth() 
u10 <- ggplot(fulldf_aei, aes(famlab, soil)) +
  geom_point() +
  stat_smooth() 
u11 <- ggplot(fulldf_aei, aes(famlab, drip)) +
  geom_point() +
  stat_smooth() 
grid.arrange(u1,u2,u3,u4,u5,u6,u7,u8,u9,u10,u11, ncol=3)


```


####Results: 


- interesting negative relationship between associated and credit and nochem. Seems to show that more associatedness and access to credit will actually lead to higher levels of agrichem useage. 

###Testing to get all on the same graph
```{r, echo=FALSE}
# (ggplot(fulldf_aei, aes(x=X)) + 
#   geom_line(aes(y=nochem, color="disp")) + 
#   geom_line(aes(y=drip, color="hp")) + 
#   geom_line(aes(y=lowtill, color="wt")))
###### issue right now is that the group aesthetic is off. Need to change stat_bin? 

```


###Regression tests with NOCHEM
```{r, warning=FALSE}
#REGRESS NO CHEM
nochem_lm <- lm(nochem ~ offfarminc + credit + lowincome + famlab + regtech + associated, fulldf_aei, , , na.exclude) # regression testing on nochem 
#na.exclude included because otherwise I cannot add the fitted values into the dataframe because there are lost observations 
# the spaces are for two other arguments that can be specified. I don't know how else to just leave them as default. 

nochem_lm # the regression results 

fulldf_aei_fit <- fulldf_aei %>% 
  mutate(nochemfit = fitted(nochem_lm)) # insert new column with the fitted values for nochem into a new dataframe that will hold the fitted values 

#ASSOCIATED
# plot with fitted values against associated
plot_nochemfit <- ggplot(fulldf_aei_fit, aes(x=associated, y = nochemfit)) +
  geom_point() +
  stat_smooth()

#plot with regular values against assocaited
plot_nochem <- ggplot(fulldf_aei, aes(associated, nochem)) +
   geom_point() +
   stat_smooth() 

grid.arrange(plot_nochemfit, plot_nochem, ncol = 2)


#CREDIT
plot_nochemfit_cred <- ggplot(fulldf_aei_fit, aes(x=credit, y = nochemfit)) +
  geom_point() +
  stat_smooth()

#plot with regular values against assocaited
plot_nochem_cred <- ggplot(fulldf_aei, aes(credit, nochem)) +
   geom_point() +
   stat_smooth() 

grid.arrange(plot_nochemfit_cred, plot_nochem_cred, ncol = 2)
```


##RESOURCES 


Visualizing distribution: 
https://flowingdata.com/2012/05/15/how-to-visualize-and-compare-distributions/

Creating a looping graph 
http://www.r-bloggers.com/ggplot2-graphics-in-a-loop/

Dealing with non-normal data 
http://www.isixsigma.com/tools-templates/normality/dealing-non-normal-data-strategies-and-tools/


