---
title: "Principle Component Analysis & Index Construction"
author: "Jill Guerra"
date: "January 5, 2016"
output: 
  html_document:
    keep_md: true 
---
###Load packages 
```{r}
library(ggplot2)
library(car) 
library(dplyr)
suppressPackageStartupMessages(library(dplyr))
library(gridExtra)
library("reshape2")
#install.packages("psych")
library(psych) # needed for chronbach's alpha
```

###Import file - Remember to change depending on what you need. 
```{r}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_01.06.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
```

###Principle Component Analysis with all components 
ALL FROM HERE: http://www.r-bloggers.com/computing-and-visualizing-pca-in-r/
```{r}

# omit NAs for this part 
rawdf_aei_omit <- na.omit(rawdf_aei)

# log transform 
log_aei <- log(rawdf_aei_omit [, 3:17]) # columns with the AE components going to be used in the index 
aei_species <- rawdf_aei_omit [, 2] # this calls the categorical variable 
# calls the Municipality names.

#Change all infinite values to NAs 
log_aei<- do.call(data.frame,lapply(log_aei, function(x) replace(x, is.infinite(x),NA))) # this changes all of them! 
# ok but the data.frame doesn't have any other things in there (only the components)

#Drop all observations with NA (thus all the infinite because they were previously changed to NA)
log_aei <- na.omit(log_aei) # shows that it is changed from 262 levels down to 139 levels. 

#Apply PCA - scale. = TRUE is highly advisable, but default is FALSE. 
log_aei_pca <- prcomp(log_aei, 
                      na.action = na.exclude, 
                      center = TRUE,               
                      scale. = TRUE) 
print(log_aei_pca)

# plot method
plot(log_aei_pca, type = "l") # this won't work unless the NAs are omitted a few lines up. 

# summary method
summary(log_aei_pca)

```

### Graphing the PCA 
```{r}
library(devtools)
#install_github("ggbiplot", "vqv") 
 
library(ggbiplot)
plot_pca <- ggbiplot(log_aei_pca, obs.scale = 1, var.scale = 1,
              ellipse = TRUE, 
              circle = TRUE)
# original code for this at group = aei_species - but I had to take it out because there were different number of observations. This is because I had to drop values in the log_aei df as prcomp would not work with NAs. 

plot_pca <- plot_pca + scale_color_discrete(name = '') + 
  theme(legend.direction = 'horizontal', legend.position = 'top')

print(plot_pca)
```

###PCA with selected components 
```{r}

# log transform 
log_aei_2 <- log(rawdf_aei_omit [, c(5,8,9,11,12,14,15)]) # columns with the selected AE components going to be used in the index 
aei_species_2 <- rawdf_aei_omit [, 2] # this calls the categorical variable 
# calls the Municipality names.

#Change all infinite values to NAs 
log_aei_2<- do.call(data.frame,lapply(log_aei_2, function(x) replace(x, is.infinite(x),NA))) # this changes all of them! 
# ok but the data.frame doesn't have any other things in there (only the components)

#Drop all observations with NA (thus all the infinite because they were previously changed to NA)
log_aei_2 <- na.omit(log_aei_2) # shows that it is changed from 262 levels down to 139 levels. 

#Apply PCA - scale. = TRUE is highly advisable, but default is FALSE. 
log_aei_pca_2 <- prcomp(log_aei_2, 
                      na.action = na.exclude, 
                      center = TRUE,               
                      scale. = TRUE) 
print(log_aei_pca_2)

# plot method
plot(log_aei_pca, type = "l") # this won't work unless the NAs are omitted a few lines up. 

# summary method
summary(log_aei_pca)

```

###AEI with brute force 
```{r create AEI with force}
#### randomly chosen variables 
# this works for the regular data.frame 
ae_index <- ((rawdf_aei$nochem + rawdf_aei$usefert +rawdf_aei$orgcomp + rawdf_aei$manure + rawdf_aei$croprot + rawdf_aei$covercrop + rawdf_aei$apm + rawdf_aei$lowtill + rawdf_aei$drip)/9) # create index! 

add_aei_df <- cbind(rawdf_aei, ae_index) # add the index into a new df 
# NAs were not excluded 

```

Drop NA observations when needed
```{r dropNAsindataframe}
#Create a new data.frame that only has rows w/o NAs
add_aei_df_dropnas <- na.omit(rawdf_aei) # 262/293 municipalities included 

```


###Check for scale consistency - Chronbach's alpha
```{r}
#  # create df with just index components (no nochem)
# thisscale <- c(5,8,9,11,12,15,16,17) # calling a selection 
# df_aei_alpha <- rawdf_aei[, thisscale] # calls out just the index variables 
# alpha(df_aei_alpha)
# # is 0.47. Not good. 
# 
# thisscale2 <- c(5,8,9,11,12,15,17) # dropped soil 
# df_aei_alpha2 <- rawdf_aei[, thisscale2] # calls out just the index variables 
# alpha(df_aei_alpha2) # 0.43 
# 
# thisscale3 <- c(5,8,9,11,12,15) # dropped soil and drip
# df_aei_alpha3 <- rawdf_aei[, thisscale3] # calls out just the index variables 
# alpha(df_aei_alpha3) # 0.44 again 


newscale <- c(8,11,12,14,15) # manure, croprotation, apm, direct planting, lowtill 
df_aei_alpha2 <- rawdf_aei[,newscale]
alpha(df_aei_alpha2)
# is 0.53

newscale3 <- c(5,9)
df_aei_alpha3 <- rawdf_aei[,newscale3]
alpha(df_aei_alpha3)

```

Results: 
scale with nochem was baaaaad. 



##Resources & Notes 

####PCA 
overview: http://www.r-bloggers.com/computing-and-visualizing-pca-in-r/
cleaning INF values: http://stackoverflow.com/questions/12188509/cleaning-inf-values-from-an-r-dataframe
* can't use is.infinite for a data.frame 

Help with diagnostics: 
http://www.ats.ucla.edu/stat/r/dae/rreg.htm