---
title: "Untitled"
author: "Jill Guerra"
date: "January 3, 2016"
output: html_document
---

Load packages 
```{r}
library(ggplot2)
library(car) 
library(dplyr)
library(gridExtra)
library("reshape2")
```

Import file
```{r}
aei<- read.csv("~/jillguerra/AEI/Census_data_formatted_for_R_01.03.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
```

Reshape data 
```{r}
aei_melted <- melt(aei) # new dataframe with melted data 
aes_index_var <- c("nochem", "croprot", "covercrop", "apm", "noconvtill", "directplanting", "lowtill", "drip") # drop of just index variables 
aes_socecon_var <- c("lowincome", "offfarminc", "association", "credit", "regtech", "famlab")# group of just the social and economic variables 

aei_melted2 <- aei_melted %>% 
  filter(variable %in% aes_index_var) # new dataframe with just the index variables 

(ggplot(aei_melted2, aes(x = X, y = value, colour = variable)) +
  geom_point()) # graph works. But now I really know that this graph should be showing the fitted values not the points. 

# not sure how to use this because the x variable doesn't make sense 

```

Checking distribution 
```{r}
str(aei)

# loop to look at the distributions. It currently works. Saves all individual graphs in png files 
nm <- names(aei)
for (i in seq_along(nm)) {
  plots <- ggplot(aei, aes_string(x=nm[i])) +
    geom_histogram()
  ggsave(plots,filename=paste("myplot",nm[i],".png",sep=""))
 
}

#var <- names(aei[1, col(i)]) # want to call row 1, column i

hist(aei$nochem)
hist(aei$croprot)
hist(aei$covercrop)
hist(aei$apm)
hist(aei$noconvtill)
hist(aei$directplanting)
hist(aei$lowtill)
hist(aei$drip)
hist(aei$lowincome) # normal 
hist(aei$offfarminc)
hist(aei$credit)
hist(aei$associated)
hist(aei$famlab)
hist(aei$regtech)

```
Results
***
- skewed to the right: nochem, croprot, covercrop, apm, low till, drip, offfarminc, regtech
- skewed to the left: soil, assoc (sort of), famlab
- credit, noconvtill and direct planting are both very strange. 

Check variability 
```{r}

var(aei$nochem)
var(aei$croprot)
var(aei$covercrop)
var(aei$apm)
var(aei$noconvtill)
var(aei$directplanting)
var(aei$lowtill)
var(aei$drip)
var(aei$soil)
var(aei$lowincome) 
var(aei$offfarminc)
var(aei$credit)
var(aei$associated)
var(aei$famlab)
var(aei$regtech)

```
Results:
***
- noconvtill and directplanting are incredibly varied compared to the others 
- lowinc, assoc, famlab and drip have no variance? Weird 

###### How do you know how much variance is ok?? 

Checking Bivariate relationships of index components 
```{r}

#No chem 
a1 <- ggplot(aei, aes(nochem, croprot)) +
  geom_point()+
  stat_smooth() 
a2 <- ggplot(aei, aes(nochem, covercrop)) +
  geom_point() +
  stat_smooth() 
a3 <- ggplot(aei, aes(nochem, apm)) +
  geom_point() +
  stat_smooth() 
a4 <- ggplot(aei, aes(nochem, noconvtill)) +
  geom_point() +
  stat_smooth() 
a5 <- ggplot(aei, aes(nochem, directplanting)) +
  geom_point() +
  stat_smooth() 
a6 <- ggplot(aei, aes(nochem, lowtill)) +
  geom_point() +
  stat_smooth() 
a7 <- ggplot(aei, aes(nochem, soil)) +
  geom_point() +
  stat_smooth() 
a8 <- ggplot(aei, aes(nochem, drip)) +
  geom_point() +
  stat_smooth()
a9 <- ggplot(aei, aes(nochem, fert)) +
  geom_point() +
  stat_smooth()
grid.arrange(a1,a2,a3,a4,a5,a6,a7,a8,a9, ncol=3)

#croprot
b1 <- ggplot(aei, aes(croprot, covercrop)) +
  geom_point() +
  stat_smooth() 
b2 <- ggplot(aei, aes(croprot, apm)) +
  geom_point() +
  stat_smooth() 
b3 <- ggplot(aei, aes(croprot, noconvtill)) +
  geom_point() +
  stat_smooth() 
b4 <- ggplot(aei, aes(croprot, directplanting)) +
  geom_point() +
  stat_smooth() 
b5 <- ggplot(aei, aes(croprot, lowtill)) +
  geom_point() +
  stat_smooth()
b6 <- ggplot(aei, aes(croprot, soil)) +
  geom_point() +
  stat_smooth()
b7 <- ggplot(aei, aes(croprot, drip)) +
  geom_point() +
  stat_smooth()
b8 <- ggplot(aei, aes(croprot, fert)) +
  geom_point() +
  stat_smooth()
grid.arrange(b1,b2,b3,b4,b5,b6,b7,b8, ncol=3) # put all the graphs into one grid 

#covercrop
c1 <- ggplot(aei, aes(covercrop, apm)) +
  geom_point() +
  stat_smooth() 
c2 <- ggplot(aei, aes(covercrop, noconvtill)) +
  geom_point() +
  stat_smooth() 
c3 <- ggplot(aei, aes(covercrop, directplanting)) +
  geom_point() +
  stat_smooth() 
c4 <- ggplot(aei, aes(covercrop, lowtill)) +
  geom_point() +
  stat_smooth()
c5 <- ggplot(aei, aes(covercrop, soil)) +
  geom_point() +
  stat_smooth()
c6 <- ggplot(aei, aes(covercrop, drip)) +
  geom_point() +
  stat_smooth()
c7 <- ggplot(aei, aes(covercrop, fert)) +
  geom_point() +
  stat_smooth()
grid.arrange(c1,c2,c3,c4,c5,c6,c7, ncol=3) # put all the graphs into one grid 

#apm 
d1 <- ggplot(aei, aes(apm, noconvtill)) +
  geom_point() +
  stat_smooth() 
d2 <- ggplot(aei, aes(apm, directplanting)) +
  geom_point() +
  stat_smooth() 
d3 <- ggplot(aei, aes(apm, lowtill)) +
  geom_point() +
  stat_smooth()
d4 <- ggplot(aei, aes(apm, soil)) +
  geom_point() +
  stat_smooth()
d5 <- ggplot(aei, aes(apm, drip)) +
  geom_point() +
  stat_smooth()
d6 <- ggplot(aei, aes(apm, fert)) +
  geom_point() +
  stat_smooth()
grid.arrange(d1,d2,d3,d4,d5,d6, ncol=3) # put all the graphs into one grid 

#skipped a few

#drip
e1 <- ggplot(aei, aes(drip, noconvtill)) +
  geom_point() +
  stat_smooth() 
e2 <- ggplot(aei, aes(drip, directplanting)) +
  geom_point() +
  stat_smooth() 
e3 <- ggplot(aei, aes(drip, lowtill)) +
  geom_point() +
  stat_smooth()
e4 <- ggplot(aei, aes(drip, soil)) +
  geom_point() +
  stat_smooth()
e5 <- ggplot(aei, aes(drip, fert)) +
  geom_point() +
  stat_smooth()
grid.arrange(e1,e2,e3,e4,e5, ncol=3)

```
Results: 
***
- very clear relatioship between nochem and fertilizer. 
- some relationship  between fert and covercrop/croprot/apm


Checking bivariate relationships of SOCECON variables 
```{r}
#credit
z <- ggplot(aei, aes(credit, associated)) +
  geom_point() +
  stat_smooth() 

z1 <- ggplot(aei, aes(credit, famlab)) +
  geom_point() +
  stat_smooth()

z2 <- ggplot(aei, aes(credit, lowincome)) +
  geom_point() +
  stat_smooth() 

z3 <- ggplot(aei, aes(credit, offfarminc)) +
  geom_point() +
  stat_smooth() 

grid.arrange(z, z1, z2,z3, ncol=3)

#associated 
y <- ggplot(aei, aes(associated, famlab)) +
  geom_point() +
  stat_smooth()

y1 <- ggplot(aei, aes(associated, lowincome)) +
  geom_point() +
  stat_smooth() 
y2 <- ggplot(aei, aes(associated, offfarminc)) +
  geom_point() +
  stat_smooth() 

grid.arrange(y, y1, y2, ncol=3)

# famlab
x <- ggplot(aei, aes(famlab, lowincome)) +
  geom_point() +
  stat_smooth() 
x1 <- ggplot(aei, aes(famlab, offfarminc)) +
  geom_point() +
  stat_smooth() 

grid.arrange(x, x1, ncol=2)

# lowincome & offfarm
(w <- ggplot(aei, aes(lowincome, offfarminc)) +
  geom_point() +
  stat_smooth()) 
```
Results
***
- credit and associated positively related 
- no other ones are related in any significant way. 

Relationship between nochem and SOCECON variables 
```{r}
n <- ggplot(aei, aes(nochem, associated)) +
  geom_point() +
  stat_smooth() 
n1 <- ggplot(aei, aes(nochem, famlab)) +
  geom_point() +
  stat_smooth()
n2 <- ggplot(aei, aes(nochem, lowincome)) +
  geom_point() +
  stat_smooth() 
n3 <- ggplot(aei, aes(nochem, offfarminc)) +
  geom_point() +
  stat_smooth() 
n4 <- ggplot(aei, aes(nochem, credit)) +
  geom_point() +
  stat_smooth() 
grid.arrange(n, n1, n2,n3,n4, ncol=3)

```
Results: 
***
- interesting negative relationship between associatedand credit and nochem. Seems to show that more associatedness and access to credit will actually lead to higher levels of agrichem useage. 


Testing to get all on the same graph
```{r}
(ggplot(aei, aes(x=X)) + 
  geom_line(aes(y=nochem, color="disp")) + 
  geom_line(aes(y=drip, color="hp")) + 
  geom_line(aes(y=lowtill, color="wt")))
###### issue right now is that the group aesthetic is off. Need to change stat_bin? 

```

Regressions
```{r}
nochem_lm <- lm(nochem ~ offfarminc + credit + lowincome + famlab + regtech +associated, aei)
aei %>% 
  mutate(nochemfit = fitted(nochem_lm)) 
###### this is ok but there are only 290 observations whereas the df has 293. How to deal with missing values? 

(ggplot(aei, aes(x=associated, y = nochemfit)) +
  geom_point())

croprot_lm <- lm(croprot ~ offfarminc + credit + lowincome + famlab + regtech +associated, aei) #run a linear regression on croprot
aei$croprot_fit <- fitted(croprot_lm) #get the fitted values and store in a new value. Won't work because the values aren't the same. 
```


Principle Component Analysis 
```{r}

```



Creating AES 
```{r}
for i in row_number(1:293) { aei %>% 
  mutate(aes = mean(aei[i,]))}

aesnm <- c("nochem", "croprot", "covercrop", "apm", "noconvtill", "directplanting", "lowtill", "soil"))

for (i in seq_along(aesnm) { aei %>% 
  mutate(aes = mean(aes)) }


##### find a way to do the average of each row and store in new column 


```


Check for scale consistency - Chronbach's alpha
```{r}
alpha
```

Checking for leverage and outliers 
```{r}


```


Create function to test all? 
```{r}
#create function to test all 
bivarplot <- function (my_x,my_y) {(ggplot(aei, aes(x = my_x, y = my_y)) +
  geom_point())}

bivarplot(my_x=aei$nochem, my_y=aei$drip)

ggplot(aei, aes(nochem, drip)) +
  geom_point()

plottest <- function(aei, x.var, y.var) {
   x <- names(aei)[x.var]
   y <- names(aei)[y.var]
   print(ggplot(aei, aes_string(x = x, y = y)) + geom_point())
}

plottest(aei, "nochem", "drip")


```

RESOURCES 
***

Visualizing distribution: 
https://flowingdata.com/2012/05/15/how-to-visualize-and-compare-distributions/

Creating a looping graph 
http://www.r-bloggers.com/ggplot2-graphics-in-a-loop/



