---
title: "Variable_diagnostics_04.06.16"
author: "Jill Guerra"
date: "April 6, 2016"
output: 
  html_document:
    keep_md: true
---
This should be used to look at the histograms, spread, variability etc of individual variables 
####PART 1: LOAD
***
####PACKAGES
```{r packages }
library(ggplot2)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gridExtra)) # for grid.arrange 
suppressPackageStartupMessages(library("moments")) # for skew & kurtosis
suppressPackageStartupMessages(library(knitr)) # for nice tables 
suppressPackageStartupMessages(library(ggbiplot)) # for PCA analysis 
suppressPackageStartupMessages(library(devtools)) # for PCA analysis as well, I believe 
suppressPackageStartupMessages(library(psych)) # needed for chronbach's alpha
suppressPackageStartupMessages(library(stats))
library(wesanderson) # form here https://github.com/karthik/wesanderson
library(broom)
library(reshape2)

```

#### DATA SET UP  - This should be in every file that I am working on)
```{r load data set}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_04.12.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
# note that this dataset was updated in a feb 22 version to only have variables that I will be working with 
```

```{r drop observations with <50 farms, results = 'hide'}

small <- c("4202453", "4202008", "4208450", "4202057", "4201950", "4206306") # these are the codes for the municipalities that have fewer than 50 farms. Names in Result_tracking Rmd. 

'%!in%' <- function(x,y)!('%in%'(x,y)) # sweet function for negating an %in% function 

# drop the municipalities that are held in the 'small' value. 
df_aei <- rawdf_aei %>% 
  filter(code %!in% small) %>% 
  droplevels()  # need to drop levels or else the new data.frame will continue to store the other factors even though they aren't being used. See Homework 5 from stats class for more about this. 

str(df_aei) # check the factor levels. It should match the #obs shown in the global environment section. If it does not then the droplevels() didn't work. 

```

```{r drop observations with NAs}
na_obs <- df_aei[rowSums(is.na(df_aei)) > 0,] # pulls out new data.frame with just the NA values

na_obs_names <- na_obs[,1]
na_obs_names

df_aei <- df_aei %>% 
  filter(code %!in% na_obs_names) %>% 
  droplevels()

nlevels(df_aei$municipality) # should be 273! 

```

###PART 2: GRAPHS FOR THE PAPER 

#### CREDIT VS ASSOCIATED 
```{r}
#CRED VS ASSOCIATED graph 
coef(lm(associated ~ credit, data = df_aei))
cred_assoc <- ggplot(df_aei, aes(x=credit, y =associated)) + 
  expand_limits(y=c(0,100)) +
  expand_limits(x=c(0,100)) +
  geom_point() + 
  geom_abline(intercept = 28.7, slope = 0.68) 
cred_assoc

ggsave("cred_vs_assoc.png", cred_assoc , scale = 1.8, height = 3, width = 4)
```

##### SHOWING DIFFERENT TRAJECTORY OF NO CHEM AND OTHER AE PRACTICES
```{r}
#REGRESSIONS AND COEFFICIENTS
a <- coef(lm(credit_access ~ cover_crop, df_aei))
b <- coef(lm(credit_access ~ crop_rotation, df_aei))
c <- coef(lm(credit_access ~ apm, df_aei))
d <- coef(lm(credit_access ~ production_diversity, df_aei))
e <- coef(lm(credit_access ~ direct_planting, df_aei))
f <- coef(lm(credit_access ~ no_agrichemicals, df_aei))

cred_coefs <- data.frame(a,b,c,d,e,f)

# create a data.frame to use in the next plot. 
cred_coefs <- t(cred_coefs) # transpose 
cred_coefs <- data.frame(cred_coefs) # take it back into a dataframe
colnames(cred_coefs) <- c("intercept", "slope") # change column names
cred_coefs["Variable"] <- c("Cover crop", "Crop rotation", "APM", "Production diversity", "Direct planting", "No agrichemicals")

#plot the lines 
cred_plot <- ggplot(df_aei, aes(x=cover_crop, y=credit_access)) + 
  geom_point(alpha = 0.001) +
  geom_abline(aes(intercept=intercept, slope=slope, color=Variable), data=cred_coefs) +  
  xlim(0,100) +
  ylab("Credit access (%)") + 
  xlab("Practice (%)") +
  labs(colour = "Regression line")  # change legend title
cred_plot
ggsave("cred_and_disaggregated.png", cred_plot , scale = 1.8, height = 3, width = 4)
```

```{r}
#REGRESSIONS AND COEFFICIENTS
g <- coef(lm(extension ~ cover_crop, df_aei))
h <- coef(lm(extension ~ crop_rotation, df_aei))
i <- coef(lm(extension ~ apm, df_aei))
j <- coef(lm(extension ~ production_diversity, df_aei))
k <- coef(lm(extension ~ direct_planting, df_aei))
l <- coef(lm(extension ~ no_agrichemicals, df_aei))

ext_coefs <- data.frame(g,h,i,j,k,l)

# create a data.frame to use in the next plot. 
ext_coefs <- t(ext_coefs) # transpose 
ext_coefs <- data.frame(ext_coefs) # take it back into a dataframe
colnames(ext_coefs) <- c("intercept", "slope") # change column names
ext_coefs["Variable"] <- c("Cover crop", "Crop rotation", "APM", "Production diversity", "Direct planting", "No agrichemicals")

#plot the lines 
ext_plot <- ggplot(df_aei, aes(x=cover_crop, y=extension)) + 
  geom_point(alpha = 0.001) +
  geom_abline(aes(intercept=intercept, slope=slope, color=Variable), ext_coefs) +  
  xlim(0,100) +
  ylab("Regular extension access (%)") + 
  xlab("Practice%") +
  labs(colour = "Regression line")  # change legend title
ext_plot
ggsave("ext_and_disaggregated.png", ext_plot , scale = 1.8, height = 3, width = 4)
```

REMEMBER: keep the scale, height and width of graphs consistent across different ones for thesis. 



####ALL INDEPENDENT AND NO CHEM 
```{r}
#REGRESSIONS AND COEFFICIENTS
cred_coef <- coef(lm(no_agrichemicals ~ credit_access, df_aei))
assoc_coef  <- coef(lm(no_agrichemicals ~ farmers_association, df_aei))
famlab_coef  <- coef(lm(no_agrichemicals ~ only_family_labour, df_aei))
offfarminc_coef  <- coef(lm(no_agrichemicals ~ off_farm_income, df_aei))
lowinc_coef  <- coef(lm(no_agrichemicals ~ low_income, df_aei))
regtech_coef  <- coef(lm(no_agrichemicals ~ extension, df_aei))

all_coefs <- data.frame(cred_coef, assoc_coef, famlab_coef, offfarminc_coef, lowinc_coef, regtech_coef)

# create a data.frame to use in the next plot. 
all_coefs <- t(all_coefs) # transpose 
all_coefs <- data.frame(all_coefs) # take it back into a dataframe
colnames(all_coefs) <- c("intercept", "slope") # change column names
all_coefs["Variable"] <- c("Credit acces", "Farmers' association", "Only family labour", "Off farm income", "Low income", "Extension")

#plot the lines 
plot <- ggplot(df_aei, aes(x=credit_access, y=no_agrichemicals)) + 
  geom_point(alpha = 0.001) +
  geom_abline(aes(intercept=intercept, slope=slope, color=Variable), data=all_coefs) + ylim(0,100) + 
  xlim(0,100) +
  ylab("Percentage of family farmers that do not use agrichemicals") + 
  xlab("Percentage")
plot

```


```{r}
#REGRESSIONS AND COEFFICIENTS
cred_coef2 <- coef(lm(cover_crop ~ credit_access, df_aei))
assoc_coef2  <- coef(lm(cover_crop ~ farmers_association, df_aei))
famlab_coef2  <- coef(lm(cover_crop ~ only_family_labour, df_aei))
offfarminc_coef2  <- coef(lm(cover_crop ~ off_farm_income, df_aei))
lowinc_coef2  <- coef(lm(cover_crop ~ low_income, df_aei))
regtech_coef2  <- coef(lm(cover_crop ~ extension, df_aei))

all_coefs2 <- data.frame(cred_coef2, assoc_coef2, famlab_coef2, offfarminc_coef2, lowinc_coef2, regtech_coef2)

# create a data.frame to use in the next plot. 
all_coefs2 <- t(all_coefs2) # transpose 
all_coefs2 <- data.frame(all_coefs2) # take it back into a dataframe
colnames(all_coefs2) <- c("intercept", "slope") # change column names
all_coefs2["Variable"] <- c("Credit acces", "Farmers' association", "Only family labour", "Off farm income", "Low income", "Extension")

#plot the lines 
plot2 <- ggplot(df_aei, aes(x=credit_access, y=no_agrichemicals)) + 
  geom_point(alpha = 0.001) +
  geom_abline(aes(intercept=intercept, slope=slope, color=Variable), data=all_coefs2) + ylim(0,100) + 
  xlim(0,100) +
  ylab("Percentage of family farmers that use cover crops") + 
  xlab("Percentage")
plot2

```

###PART 3: BACKGROUND CHECKS
***
#####HISTOGRAMS
```{r}
# make sure that this is pulling from the clean dataset (no small farms, no NAs - i.e. the data that is used in the regression) 
a <- ggplot(df_aei, aes(x = covercrop)) +
 geom_histogram()
b <- ggplot(df_aei, aes(x = croprot)) +
 geom_histogram()
# c <- ggplot(df_aei, aes(x = orgcomp)) +
#  geom_histogram()
d <- ggplot(df_aei, aes(x = manure)) +
 geom_histogram()
e <- ggplot(df_aei, aes(x = apm)) +
 geom_histogram()
f <- ggplot(df_aei, aes(x = diverse)) +
 geom_histogram()
g <- ggplot(df_aei, aes(x = straw)) +
 geom_histogram()
h<- ggplot(df_aei, aes(x = nochem)) +
  geom_histogram()

p <- ggplot(df_aei, aes(x = famlab)) +
  geom_histogram()
q <- ggplot(df_aei, aes(x = associated)) +
 geom_histogram()
r <- ggplot(df_aei, aes(x = lowincome)) +
 geom_histogram()
s <- ggplot(df_aei, aes(x = regtech)) +
 geom_histogram()
t <- ggplot(df_aei, aes(x = credit)) +
 geom_histogram()
u <- ggplot(df_aei, aes(x = offfarminc)) +
  geom_histogram()

# note that the alphabet is split because I took this from a previous file 
grid.arrange(a,b,d,e,f,g,h,p,q,r,s,t,u, ncol=3)

```

##### SKEW, KURT, VARIANCE
```{r data checks}
# create dataframe without the first two columns because they aren't numbers 
df_onlynum <- df_aei[,3:(ncol(df_aei))] # drop the first two columns 

#skewness 
skew <- apply(df_onlynum, 2, skewness, na.rm=TRUE) # call correct df, 2 means looking at columns (1 would indicate looking rows), skewness is the function applied, ignore NAs 

#kurtosis
kurt <- apply(df_onlynum, 2, kurtosis, na.rm=TRUE) # df, looking at columns, kurtosis is function, ignore NAs

#variance 
variance <- apply(df_onlynum, 2, var, na.rm=TRUE)# df, looking at columns, variance is function, ignore NAs

```

```{r table }
#combine values lists into a dataframe 
data_checks <- cbind(kurt, skew, variance) 
knitr::kable(data_checks) # nice table with all the data 

```

##### CORRELATIONS
```{r}
cor(df_aei$diverse, df_aei$credit) # = 0.57
cor(df_aei$diverse, df_aei$regtech) # = NONE
cor(df_aei$diverse, df_aei$associated) # = 0.4
cor(df_aei$diverse, df_aei$lowincome) # 0.52
cor(df_aei$regtech, df_aei$credit) # = 0.39
cor(df_aei$regtech, df_aei$associated) # = 0.32
cor(df_aei$credit, df_aei$associated) # = 0.67
cor(df_aei$straw, df_aei$manure) # = 0.23
cor(df_aei$straw, df_aei$covercrop) # = 0.10
cor(df_aei$manure, df_aei$manure)
cor(df_aei$covercrop, df_aei$croprot)
cor(df_aei$low_income, df_aei$only_family_labour) # = 0.14
cor(df_aei$credit, df_aei$low_income) # = 0.16
cor(df_aei$credit, df_aei$only_family_labour) # = -0.17
cor(df_aei$credit, df_aei$off_farm_income) # -0.51


summary(lm(farmers_association ~ credit_access, df_aei))
summary(lm(extension ~ credit_access, df_aei))
summary(lm(credit_access~ farmers_association, df_aei))


```

#### REGRESSIONS WITH INDIVIDUAL DEPENDENT VARIABLES
```{r}
#COVER CROP 
lm_covercrop <- lm(covercrop ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_covercrop)
plot(lm_covercrop)

#CROP ROTATION 
lm_croprot <- lm(croprot ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_croprot)
plot(lm_croprot)

#MANURE
lm_manure <- lm(manure ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_manure)
plot(lm_manure)

#APM
lm_apm <- lm(apm ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_apm)
plot(lm_apm)

#DIVERSE
lm_diverse <- lm(diverse ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_diverse)
plot(lm_diverse)

#STRAW
lm_straw <- lm(straw ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_straw)
plot(lm_straw)

# NOCHEM 
lm_nochem <- lm(nochem ~ lowincome + credit + regtech + associated + famlab + offfarminc, df_aei)
summary(lm_nochem)
plot(lm_nochem)

```

Thes correlations point to a moderate-strong relationship between production diversity and credit. So diversification of acitivies requires some access to credit 

```{r testing some regression line graphs}

plot(df_aei$direct_planting, df_aei$no_agrichemicals)
abline(lm(df_aei$diverse~df_aei$credit))

```

