---
title: "Variable_diagnostics_04.06.16"
author: "Jill Guerra"
date: "April 6, 2016"
output: html_document
---
This should be used to look at the histograms, spread, variability etc of individual variables 
####PART 1: LOAD
***
####PACKAGES
```{r packages }
library(ggplot2)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gridExtra)) # for grid.arrange 
suppressPackageStartupMessages(library("moments")) # for skew & kurtosis
suppressPackageStartupMessages(library(knitr)) # for nice tables 
suppressPackageStartupMessages(library(ggbiplot)) # for PCA analysis 
suppressPackageStartupMessages(library(devtools)) # for PCA analysis as well, I believe 
suppressPackageStartupMessages(library(psych)) # needed for chronbach's alpha
suppressPackageStartupMessages(library(stats)) 
```

#### DATA SET UP  - This should be in every file that I am working on)
```{r load data set}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_04.10.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
# note that this dataset was updated in a feb 22 version to only have variables that I will be working with 
```

```{r drop observations with <50 farms, results = 'hide'}

small <- c("4202453", "4202008", "4208450", "4202057", "4201950", "4206306") # these are the codes for the municipalities that have fewer than 50 farms. Names in Result_tracking Rmd. 

'%!in%' <- function(x,y)!('%in%'(x,y)) # sweet function for negating an %in% function 

# drop the municipalities that are held in the 'small' value. 
df_aei <- rawdf_aei %>% 
  filter(code %!in% small) %>% 
  droplevels()  # need to drop levels or else the new data.frame will continue to store the other factors even though they aren't being used. See Homework 5 from stats class for more about this. 

str(df_aei) # check the factor levels. It should match the #obs shown in the global environment section. If it does not then the droplevels() didn't work. 

```

```{r drop observations with NAs}
na_obs <- df_aei[rowSums(is.na(df_aei)) > 0,] # pulls out new data.frame with just the NA values

na_obs_names <- na_obs[,1]

df_aei <- df_aei %>% 
  filter(code %!in% na_obs_names) %>% 
  droplevels()

nlevels(df_aei$municipality) # should be 273! 

```


###PART 2: DATA CHECKS
***
#####HISTOGRAMS
```{r}
# make sure that this is pulling from the clean dataset (no small farms, no NAs - i.e. the data that is used in the regression) 
a <- ggplot(df_aei, aes(x = covercrop)) +
 geom_histogram()
b <- ggplot(df_aei, aes(x = croprot)) +
 geom_histogram()
# c <- ggplot(df_aei, aes(x = orgcomp)) +
#  geom_histogram()
d <- ggplot(df_aei, aes(x = manure)) +
 geom_histogram()
e <- ggplot(df_aei, aes(x = apm)) +
 geom_histogram()
f <- ggplot(df_aei, aes(x = diverse)) +
 geom_histogram()
g <- ggplot(df_aei, aes(x = straw)) +
 geom_histogram()
h<- ggplot(df_aei, aes(x = nochem)) +
  geom_histogram()

p <- ggplot(df_aei, aes(x = famlab)) +
  geom_histogram()
q <- ggplot(df_aei, aes(x = associated)) +
 geom_histogram()
r <- ggplot(df_aei, aes(x = lowincome)) +
 geom_histogram()
s <- ggplot(df_aei, aes(x = regtech)) +
 geom_histogram()
t <- ggplot(df_aei, aes(x = credit)) +
 geom_histogram()
u <- ggplot(df_aei, aes(x = offfarminc)) +
  geom_histogram()

# note that the alphabet is split because I took this from a previous file 
grid.arrange(a,b,d,e,f,g,h,p,q,r,s,t,u, ncol=3)

```

##### SKEW, KURT, VARIANCE
```{r data checks}
# create dataframe without the first two columns because they aren't numbers 
df_onlynum <- df_aei[,3:(ncol(df_aei))] # drop the first two columns 

#skewness 
skew <- apply(df_onlynum, 2, skewness, na.rm=TRUE) # call correct df, 2 means looking at columns (1 would indicate looking rows), skewness is the function applied, ignore NAs 

#kurtosis
kurt <- apply(df_onlynum, 2, kurtosis, na.rm=TRUE) # df, looking at columns, kurtosis is function, ignore NAs

#variance 
variance <- apply(df_onlynum, 2, var, na.rm=TRUE)# df, looking at columns, variance is function, ignore NAs

```

```{r table }
#combine values lists into a dataframe 
data_checks <- cbind(kurt, skew, variance) 
knitr::kable(data_checks) # nice table with all the data 

```

##### CORRELATIONS
```{r}
cor(df_aei$diverse, df_aei$credit) # = 0.57
cor(df_aei$diverse, df_aei$regtech) # = NONE
cor(df_aei$diverse, df_aei$associated) # = 0.4
cor(df_aei$diverse, df_aei$lowincome) # 0.52
cor(df_aei$regtech, df_aei$credit) # = 0.39
cor(df_aei$regtech, df_aei$associated) # = 0.32
cor(df_aei$credit, df_aei$associated) # = 0.67
```

#### REGRESSIONS WITH INDIVIDUAL DEPENDENT VARIABLES
```{r}
#COVER CROP 
lm_covercrop <- lm(covercrop ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_covercrop)
plot(lm_covercrop)

#CROP ROTATION 
lm_croprot <- lm(croprot ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_croprot)
plot(lm_croprot)

#MANURE
lm_manure <- lm(manure ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_manure)
plot(lm_manure)

#APM
lm_apm <- lm(apm ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_apm)
plot(lm_apm)

#DIVERSE
lm_diverse <- lm(diverse ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_diverse)
plot(lm_diverse)

#STRAW
lm_straw <- lm(straw ~ lowincome + credit + regtech + associated, df_aei)
summary(lm_straw)
plot(lm_straw)

# NOCHEM 
lm_nochem <- lm(nochem ~ lowincome + credit + regtech + associated + famlab + offfarminc, df_aei)
summary(lm_nochem)
plot(lm_nochem)
```

Thes correlations point to a moderate-strong relationship between production diversity and credit. So diversification of acitivies requires some access to credit/ 