---
title: "Regression_diagnostics_02.22.2016"
author: "Jill Guerra"
date: "February 22, 2016"
output: 
  html_document:
    keep_md: true 
---

```{r load data set}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_02.22.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
```

```{r drop observations with <50 farms}

small <- c("4202453", "4202008", "4208450", "4202057", "4201950", "4206306") # these are the codes for the municipalities that have fewer than 50 farms. Names in Result_tracking Rmd. 

'%!in%' <- function(x,y)!('%in%'(x,y)) # sweet function for negating an %in% function 

# drop the municipalities that are held in the 'small' value. 
df_aei <- rawdf_aei %>% 
  filter(code %!in% small) %>% 
  droplevels()  # need to drop levels or else the new data.frame will continue to store the other factors even though they aren't being used. See Homework 5 from stats class for more about this. 

str(df_aei) # check the factor levels. It should match the #obs shown in the global environment section. If it does not then the droplevels() didn't work. 

```

```{r drop observations with NAs}
df_aei <- df_aei %>% 
  na.omit() %>% 
  droplevels() # take out observations that have an NA in any variable. There are 14 with NAs. 

str(df_aei)
```
```{r First create the index and bind}
#Create the index with manure
agscores <- ((df_aei$manure + df_aei$apm + df_aei$croprot + df_aei$straw + df_aei$diverse + df_aei$covercrop)/6) # testing one score set 

# bind the scores onto the original dataframe 
df_aei_scores <- cbind(df_aei, agscores) 
df_aei_scores

#regress according to the scores
lm_agscores <- lm(agscores ~ famlab + lowincome + associated + regtech + credit + offfarminc, df_aei_scores)
summary(lm_agscores)
```

```{r Second index without manure }
#Create the index without manure
agscores2 <- ((df_aei$apm + df_aei$croprot + df_aei$straw + df_aei$diverse + df_aei$covercrop)/5) # testing one score set 

# bind the scores onto the original dataframe 
df_aei_scores2 <- cbind(df_aei, agscores2) 
df_aei_scores2

#regress according to the scores
lm_agscores2 <- lm(agscores2 ~ famlab + lowincome + associated + regtech + credit + offfarminc, df_aei_scores2)
summary(lm_agscores)
# Essentially the same results as without manure. 
```


Source for looking at diagnostics: http://www.statmethods.net/stats/rdiagnostics.html

#Outliers 
```{r Outliers}
#This uses the scale that includes manure 
outlierTest(lm_agscores) 
qqPlot(lm_agscores, main="QQ Plot") 
leveragePlots(lm_agscores)
```

```{r}
summary(lm_agscores) # regression that i want to use 

opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) # not quite sure what this does but got it from ats.ucla website shown below 
plot(lm_agscores, las = 1) # highlights the observations that may be problematic 
# for this run it is: 1, 10, 31, 109, 206,287

par(opar)

```

Results show: 
- Normal QQ: shows normality 
- Residuals vs. Fitted: Generally ok. (need to see a band around the horizontal line) 10, 31, 109 higlighted. 
- Scale- Location: no trend to the residuals - this is what we want. However the same cases highlighted in as the residuals vs. fitted plot 
- Residuals vs. Leverage: fairly symetrical around zero - good. 

```{r Cooks D }
cd_full <- cooks.distance(lm_agscores) # run cook's D looking for leverage and residual
cd_res <- stdres(lm_agscores) #  calculate student residuals
diag_full <- cbind(df_aei_scores, cd_full, cd_res) # add cooks D and student residuals to the dataframe


#Cook's D 
diag_full[cd_full > 4/(273-7-1), ] #pull out on the cook's D's that are great than 
####### here n = 273, k = 6 (6 independent variables, 1 dependent?) 
####### Is this right? May have the wrong degress of freedom 
#If so: 1,10,13,31,62,69,109,125,150,156,160,206,228,260,272,287
# if it is 7 the same cases were pulled out. 


#Residuals  
rabs <- abs(cd_res) # absolute value of the residuals
diag_full2 <- cbind(diag_full, rabs) # bind these residuals with the previous df
diag_full2_sorted <- diag_full2[order(-rabs), ]
diag_full2_sorted[1:10, ] # this shows the largest residuals 
# turn out to be 1,10,13,31,109,150,156,232,260,287

```
Therefore based on these analyises: 
Would need to remove:
1,10,13,31,109,150,156,206,232,260,287
Which are: 
4200051
4200754
4201000
4202206
4207650
4210704
4211108
4215109
4217006
4218905
4219853


```{r filter out the bad observations}

df_aei_scores_filtered <- df_aei_scores[-c(1, 10, 13, 31, 109, 150, 156, 206, 232, 260, 287), ] # this points ot the rows that you want to delete. Not columns 

df_aei_scores_filtered <- df_aei_scores %>% 
  filter(code != c("4200051", "4200754", "4201000", "4202206", "4207650", "4210704", "4211108", "4215109", "4217006", "4218905", "4219853"))


```

