---
title: "Regression"
author: "Jill Guerra"
date: "January 8, 2016"
output: html_document
---
Need to have finalized excel spreadsheet here with sustainability index 
Steps: 
Regression 
Summary of regression 
Residuals
Leverage
Outliers 
Cooks D 

##SetUp
###Load packages 
```{r}
library(ggplot2)
library(car) 
suppressPackageStartupMessages(library(dplyr))
library(gridExtra)
library("reshape2")
#install.packages("MASS")
library("MASS")
```

###Import file - Remember to change depending on what you need. 
```{r}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_01.06.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
```

###AEI creation
```{r}
ae_index <- ((rawdf_aei$nochem + rawdf_aei$usefert +rawdf_aei$orgcomp + rawdf_aei$manure + rawdf_aei$croprot + rawdf_aei$covercrop + rawdf_aei$apm + rawdf_aei$lowtill + rawdf_aei$drip)/9) # create index! 

df_aei<- cbind(rawdf_aei, ae_index) # add the index into a new df 
df_aei_omit_nas <- na.omit(df_aei)

```

###Regression using all Socio-econominc variables
```{r testing regressions}
# full dataset 
lm_full <- lm(ae_index ~ famlab + lowincome + associated + regtech + credit + offfarminc, df_aei)
lm_full

```

###Checking Standardized Residuals
```{r residuals}
 
st_res <- rstandard(lm_full) #pulls out the standard residuals from the regression

#ASSOCIATED
plot_lm_full_stred <- ggplot(df_aei_omit_nas, aes(associated, st_res)) +
  geom_point()

plot_lm_full_stred

#FAMLAB 
plot_lm_full_stred2 <- ggplot(df_aei_omit_nas, aes(famlab, st_res)) +
  geom_point()

plot_lm_full_stred2

#CREDIT
plot_lm_full_stred3 <- ggplot(df_aei_omit_nas, aes(credit, st_res)) +
  geom_point()

plot_lm_full_stred3

#OFFFARMINCOME

plot_lm_full_stred4 <- ggplot(df_aei_omit_nas, aes(offfarminc, st_res)) +
  geom_point()

plot_lm_full_stred4

#LOWINCOME
plot_lm_full_stred5 <- ggplot(df_aei_omit_nas, aes(lowincome, st_res)) +
  geom_point()

plot_lm_full_stred5

#REGTECH
plot_lm_full_stred6 <- ggplot(df_aei_omit_nas, aes(regtech, st_res)) +
  geom_point()

plot_lm_full_stred6

```

####Results:
- when using ((rawdf_aei$nochem + rawdf_aei$usefert +rawdf_aei$orgcomp + rawdf_aei$manure + rawdf_aei$croprot + rawdf_aei$covercrop + rawdf_aei$apm + rawdf_aei$lowtill + rawdf_aei$drip)/9)

- Only issue: famlab is somewhat heteroskedastic

###Plot residuals, show leverage 
```{r diagnostics on full}
summary(lm_full)

opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) # not quite sure what this does but got it from ats.ucla website shown below 
plot(lm_full, las = 1) # highlights the observations that may be problematic 

par(opar)
```
###Cases that may be an issue based on the previous graph 
```{r}
# because this first run hightlighted 88, 100, 47, 227 as potential issues, the next line picks them out. 
df_aei[c(88,100,47,227), 1:2]

```

###Cook's D and Studentized residuals
```{r}
cd_full <- cooks.distance(lm_full) # run cook's D looking for leverage and residual
cd_res <- stdres(lm_full) #  calculate student residuals
diag_full <- cbind(df_aei_omit_nas, cd_full, cd_res) # add cooks D and student residuals to the dataframe
##### had to use the df with no NAs or they wouldn't be the same length 
##### find a way to do it with NAs? 

#Cook's D 
diag_full[cd_full > 4/(293-6-1), ] #pull out on the cook's D's that are great than 
####### here n = 293, k = 6 (6 independent variables, 1 dependent?) 
# gives back 1,2,10,33,47,70,76,88,100,105,113,118,124,130,131,148,155,170,179,209,212,227,248

#Residuals  
rabs <- abs(cd_res) # absolute value of the residuals
diag_full2 <- cbind(diag_full, rabs) # bind these residuals with the previous df
diag_full2_sorted <- diag_full2[order(-rabs), ]
diag_full2_sorted[1:10, ] # this shows the largest residuals 
# turn out to be 10, 88, 47, 131,70, 33, 118, 227, 170, 124 

```


### Same analysis as above but with NAs omitted 
```{r no NAs}
# no observations with NAs
lm_na_omitted <- lm(ae_index ~ famlab + lowincome + associated + regtech + credit + offfarminc, df_aei_omit_nas) # testing if NAs are omitted. 
lm_na_omitted 

summary(lm_na_omitted)

opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) # not quite sure what this does but got it from ats.ucla website shown below 
plot(lm_na_omitted, las = 1) # highlights the observations that may be problematic 
# shows the same values as above 
par(opar)
```

```{r subset}
# get a subset showing all the observations with NA values 
# new_DF <- subset(df_aei, is.na(df_aei$ae_index))
# subset()

# almost all NAs in the ae_index are driven by drip irrigation 
```

