---
title: "Scale_Regression_Checks"
author: "Jill Guerra"
date: "April 6, 2016"
output: 
  html_document:
    keep_md: true 
---
UPDATED: April 6


###PART 1: LOAD DATA, CREATE SCALE
***
This section loads the packages, imports data and cleans the data of small farms and observations with NA values 
####PACKAGES
```{r packages }
library(ggplot2)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gridExtra)) # for grid.arrange 
suppressPackageStartupMessages(library("moments")) # for skew & kurtosis
suppressPackageStartupMessages(library(knitr)) # for nice tables 
suppressPackageStartupMessages(library(ggbiplot)) # for PCA analysis 
suppressPackageStartupMessages(library(devtools)) # for PCA analysis as well, I believe 
suppressPackageStartupMessages(library(psych)) # needed for chronbach's alpha
```

#### DATA SET UP  - This should be in every file that I am working on)
```{r load data set}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_02.22.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
# note that this dataset was updated in a feb 22 version to only have variables that I will be working with 
```

```{r drop observations with <50 farms, results = 'hide'}

small <- c("4202453", "4202008", "4208450", "4202057", "4201950", "4206306") # these are the codes for the municipalities that have fewer than 50 farms. Names in Result_tracking Rmd. 

'%!in%' <- function(x,y)!('%in%'(x,y)) # sweet function for negating an %in% function 

# drop the municipalities that are held in the 'small' value. 
df_aei <- rawdf_aei %>% 
  filter(code %!in% small) %>% 
  droplevels()  # need to drop levels or else the new data.frame will continue to store the other factors even though they aren't being used. See Homework 5 from stats class for more about this. 

str(df_aei) # check the factor levels. It should match the #obs shown in the global environment section. If it does not then the droplevels() didn't work. 

```

```{r drop observations with NAs}
df_aei <- df_aei %>% 
  na.omit() %>% 
  droplevels() # take out observations that have an NA in any variable 

str(df_aei)
```

###PART 2: SCALE CREATION 
***
This section will define the Agscores scale and bind it to the original dataframe, but stored in a new dataframe ('df_aei_score')

####SCALE  
```{r}
#columns from current dataset:

# current column numbers for orgcomp (3), manure (4), covercrop (5), croprotation (6), apm(7), production diversity (8) straw(9)
ae_scale_test <- df_aei[,c(4:9)] # this one looks the best. It excludes organic compost because it as negatively related in the alpha of the scale in which it was included 
alpha(ae_scale_test)
# chronbach's is 0.73

```

```{r create the index and bind, results='hide'}
#Creating scores
agscores <- ((df_aei$apm +df_aei$croprot + df_aei$straw + df_aei$manure + df_aei$covercrop + df_aei$diverse)/6) # testing one score set 

# bind the scores onto the original dataframe but store as a new dataframe
df_aei_scores <- cbind(df_aei, agscores) 
df_aei_scores
```

###PART 3: REGRESSION
***
#### REGRESSIONS

Regression with all independent variables 
```{r regression with each separate}
lm_sep <- lm(agscores ~ lowincome + credit + regtech + associated, df_aei_scores)
summary(lm_sep)
```

```{r regression 2x2}
lm_2by2_1 <- lm(agscores ~ lowincome + credit, df_aei_scores)
summary(lm_2by2_1)

lm_2by2_2 <- lm(agscores ~ regtech + associated, df_aei_scores)
summary(lm_2by2_2)
```

ANOVA 
```{r}
anova(lm_sep)
```

PLOT REGRESSION
```{r}
plot(lm_sep)

```




MAPS! 
link to blog using brazilian municipalities shapefile 
https://dioferrari.wordpress.com/2014/11/27/plotting-maps-using-r-example-with-brazilian-municipal-level-data/



