---
title: "Scale_Regression_Checks"
author: "Jill Guerra"
date: "April 12, 2016"
output: 
  html_document:
    keep_md: true 
---
UPDATED: April 12


###PART 1: LOAD DATA, CREATE SCALE
***
This section loads the packages, imports data and cleans the data of small farms and observations with NA values 
####PACKAGES
```{r packages }
library(ggplot2)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gridExtra)) # for grid.arrange 
suppressPackageStartupMessages(library("moments")) # for skew & kurtosis
suppressPackageStartupMessages(library(knitr)) # for nice tables 
suppressPackageStartupMessages(library(ggbiplot)) # for PCA analysis 
suppressPackageStartupMessages(library(devtools)) # for PCA analysis as well, I believe 
suppressPackageStartupMessages(library(psych)) # needed for chronbach's alpha
suppressPackageStartupMessages(library(stats)) 
suppressPackageStartupMessages(library(stargazer)) 


```

#### DATA SET UP  - This should be in every file that I am working on)
```{r load data set}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_04.12.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
# note that this dataset was updated in a feb 22 version to only have variables that I will be working with 
```

```{r drop observations with <50 farms, results = 'hide'}

small <- c("4202453", "4202008", "4208450", "4202057", "4201950", "4206306") # these are the codes for the municipalities that have fewer than 50 farms. Names in Result_tracking Rmd. 

'%!in%' <- function(x,y)!('%in%'(x,y)) # sweet function for negating an %in% function 

# drop the municipalities that are held in the 'small' value. 
df_aei <- rawdf_aei %>% 
  filter(code %!in% small) %>% 
  droplevels()  # need to drop levels or else the new data.frame will continue to store the other factors even though they aren't being used. See Homework 5 from stats class for more about this. 

str(df_aei) # check the factor levels. It should match the #obs shown in the global environment section. If it does not then the droplevels() didn't work. 

```

```{r drop observations with NAs}
na_obs <- df_aei[rowSums(is.na(df_aei)) > 0,] # pulls out new data.frame with just the NA values

na_obs_names <- na_obs[,1]

df_aei <- df_aei %>% 
  filter(code %!in% na_obs_names) %>% 
  droplevels()

nlevels(df_aei$municipality) # should be 273! 

```

###PART 2: SCALE CREATION 
***
This section will define the Agscores scale and bind it to the original dataframe, but stored in a new dataframe ('df_aei_score')

####SCALE  
```{r}
#columns from current dataset:

# current column numbers for orgcomp (3), manure (4), cover_crop (5), crop_rotationation (6), apm(7), production diversity (8) direct_planting(9)
ae_scale_old <- df_aei[,c(4:9)] # this one looks the best. It excludes organic compost because it as negatively related in the alpha of the scale in which it was included 
alpha(ae_scale_old)
# chronbach's is 0.73

# new scae that looks pretty good. 
ae_scale <- df_aei[,c(5:9)] 
alpha(ae_scale) #= 0.74

cor(df_aei$direct_planting, df_aei$credit_access)

```

```{r create the index and bind, results='hide'}
#Creating scores
agscores <- ((df_aei$apm +df_aei$crop_rotation + df_aei$direct_planting + df_aei$manure + df_aei$cover_crop + df_aei$production_diversity)/6) # testing one score set 

str(agscores)

# bind the scores onto the original dataframe but store as a new dataframe
df_aei_scores <- cbind(df_aei, agscores) 
df_aei_scores
write.csv(df_aei_scores, file = "df_aei_scores.csv")
```

###PART 3: INITIAL REGRESSIONS
***
#### REGRESSIONS - without any leverage/outliers removed 

Regression with all independent variables 
```{r regression with all independent}

lm_sep1 <- lm(agscores ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei_scores)
summary(lm_sep1)
```

```{r regression with some independent}
lm_sep2 <- lm(agscores ~ low_income + credit_access + extension+ farmers_association, df_aei_scores)
summary(lm_sep2)
```


```{r regression 2x21}
lm_2by2_1 <- lm(agscores ~ low_income + credit_access, df_aei_scores)
summary(lm_2by2_1)

lm_2by2_2 <- lm(agscores ~ extension+ farmers_association, df_aei_scores)
summary(lm_2by2_2)
```

ANOVA 
```{r}
anova(lm_sep1)
```

PLOT REGRESSION
```{r}
plot(lm_sep1)
```

#### REGRESSIONS WITH INDIVIDUAL DEPENDENT VARIABLES
```{r}
#COVER CROP 
lm_cover_crop <- lm(cover_crop ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei)
summary(lm_cover_crop)

#CROP ROTATION 
lm_crop_rotation <- lm(crop_rotation ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei)
summary(lm_crop_rotation)

#MANURE
lm_manure <- lm(manure ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei)
summary(lm_manure)

#APM
lm_apm <- lm(apm ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei)

#production_diversity
lm_production_diversity <- lm(production_diversity ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei)
summary(lm_production_diversity)

#direct_planting
lm_direct_planting <- lm(direct_planting ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei)
summary(lm_direct_planting)

#no_agrichemicals
lm_no_agrichemicals <- lm(no_agrichemicals ~ low_income + credit_access + extension+ farmers_association + only_family_labour + off_farm_income, df_aei)
summary(lm_no_agrichemicals)

```

####INDIVIDUAL INDEPENDENT VARIABLES ON AG SCORES
```{r testing some regression plots on scores}
pl_cred <- ggplot(df_aei_scores, aes(x=agscores, y = credit_access)) +
  geom_point() +
  geom_smooth(method=lm)

pl_assoc <- ggplot(df_aei_scores, aes(x=agscores, y = farmers_association)) +
  geom_point() +
  geom_smooth(method=lm)

pl_extension<- ggplot(df_aei_scores, aes(x=agscores, y = extension)) +
  geom_point() +
  geom_smooth(method=lm)

pl_low_income <- ggplot(df_aei_scores, aes(x=agscores, y = low_income)) +
  geom_point() +
  geom_smooth(method=lm)

pl_offfarm <- ggplot(df_aei_scores, aes(x=agscores, y = off_farm_income)) +
  geom_point() +
  geom_smooth(method=lm)

pl_only_family_labour <- ggplot(df_aei_scores, aes(x=agscores, y = only_family_labour)) +
  geom_point() +
  geom_smooth(method=lm)

grid.arrange(pl_cred, pl_assoc, pl_extension, pl_offfarm, pl_low_income, pl_only_family_labour, ncol=3)

```

### PART 4: REGRESSION CHECKS 
***

####RESIDUALS
```{r residuals}
 st_res <- rstandard(lm_sep1) #pulls out the standard residuals from the regression

#Residuals for all independent variables 
stres_a <- ggplot(df_aei_scores, aes(farmers_association, st_res)) +
  geom_point() +
  stat_smooth()

stres_c <- ggplot(df_aei_scores, aes(credit_access, st_res)) +
  geom_point() +
  stat_smooth()

stres_i <- ggplot(df_aei_scores, aes(low_income, st_res)) +
  geom_point() +
  stat_smooth()

stres_t <- ggplot(df_aei_scores, aes(extension, st_res)) +
  geom_point() +
  stat_smooth()

stres_fl <- ggplot(df_aei_scores, aes(only_family_labour, st_res)) +
  geom_point() +
  stat_smooth()

stres_of <- ggplot(df_aei_scores, aes(off_farm_income, st_res)) +
  geom_point() +
  stat_smooth()

grid.arrange(stres_a, stres_c, stres_i, stres_t, stres_fl, stres_of, ncol=2)
```

#### RESIDUALS & LEVERAGE
```{r diagnostics on full}
summary(lm_sep1)

opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0)) # not quite sure what this does but got it from ats.ucla website shown below 
plot(lm_sep1, las = 1) # highlights the observations that may be problematic 

par(opar)
```
###LIST OF PROBLEM CASES 
```{r}
# Cases identified April 7th with data set excluding small farms and NAs and an ag scale of cover crop, crop rot, apm, manure, direct_planting and production_diversity
# enter observation numbers and display the 
df_aei_scores[c(10,29,58,105,273), 1:2]

```
###Cook's D and Studentized residuals
```{r cooks d}
cd <- cooks.distance(lm_sep1) # run cook's D looking for leverage and residual
sres <- rstandard(lm_sep1) #  calculate standardized residuals
df_diag_sep <- cbind(df_aei_scores, cd, sres) # add cooks D and student residuals to the dataframe

#COOK'S D
cooks_d <- df_diag_sep[cd > 4/(268), ] #pull out on the cook's D's that are beyond the hypothetical cutoff. Degrees of freedom for lm_sep is 268 (from the summary output)

#RESIDUALS
rabs <- abs(sres) # absolute value of the residuals
df_diag_sep <- cbind(df_diag_sep, rabs) # bind these residuals with the previous df
df_diag_sep <- df_diag_sep[order(-rabs), ] # reorder according to absolute value residuals
big_residuals <- df_diag_sep[1:10,] # this shows the largest residuals 
```

####RESULTS 
```{r tables with residuals and cooks D results}
 
knitr::kable(cooks_d[,c(1, 2, 17)]) 
knitr::kable(big_residuals[,c(1, 2, 19)])
```

####LIST OF PROBLEM CASES 
Municipalities that showed up on more than 1 of the above tables or from the earlier plots 
```{r}
prob_cases <- df_aei_scores[c(10, 21,29,58,77,145,246,258,273), 1:2]
knitr::kable(prob_cases) # nice table of problem cases 
```

###PART 5: RESPECIFICATION 
***
Rerun the regressions as performed earlier but without the leverage and outliers. Remember that the ag scores are already defined from earlier, so do not need to add again. 

####REMOVE PROBLEM CASES
```{r}
prob_cases_codes <- prob_cases[,1] # pull out just the code names of the cases identified in the previous chunk 

rerun_df_aei_scores <- df_aei_scores %>% 
  filter(code %!in% prob_cases_codes) %>% # remove all cases identified in previous chunk
  droplevels() # drop factor levels 

str(rerun_df_aei_scores)
```

#####REGRESSION
```{r regression with each separate}
lm_sep_rr <- lm(agscores ~ low_income + credit_access + extension+ farmers_association, rerun_df_aei_scores)
summary(lm_sep_rr)
```

```{r regression 2x2}
lm_2by2_1_rr <- lm(agscores ~ low_income + credit_access, rerun_df_aei_scores)
summary(lm_2by2_1_rr)

lm_2by2_2_rr <- lm(agscores ~ extension+ farmers_association, rerun_df_aei_scores)
summary(lm_2by2_2_rr)
```

ANOVA 
```{r}
anova(lm_sep_rr)
```

PLOT REGRESSION
```{r}
plot(lm_sep_rr)
```

#### REGRESSIONS WITH INDIVIDUAL DEPENDENT VARIABLES
```{r}
#COVER CROP 
lm_cover_crop_rr <- lm(cover_crop ~ low_income + credit_access + extension+ farmers_association, rerun_df_aei_scores)
summary(lm_cover_crop_rr)
plot(lm_cover_crop_rr)

#CROP ROTATION 
lm_crop_rotation_rr <- lm(crop_rotation ~ low_income + credit_access + extension+ farmers_association, rerun_df_aei_scores)
summary(lm_crop_rotation_rr)
plot(lm_crop_rotation_rr)

#MANURE
lm_manure_rr <- lm(manure ~ low_income + credit_access + extension+ farmers_association, rerun_df_aei_scores)
summary(lm_manure_rr)
plot(lm_manure_rr)

#APM
lm_apm_rr <- lm(apm ~ low_income + credit_access + extension+ farmers_association, rerun_df_aei_scores)
summary(lm_apm_rr)
plot(lm_apm_rr)

#production_diversity
lm_production_diversity_rr <- lm(production_diversity ~ low_income + credit_access + extension+ farmers_association, rerun_df_aei_scores)
summary(lm_production_diversity_rr)
plot(lm_production_diversity_rr)

#direct_planting
lm_direct_planting_rr <- lm(direct_planting ~ low_income + credit_access + extension+ farmers_association, rerun_df_aei_scores)
summary(lm_direct_planting_rr)
plot(lm_direct_planting_rr)

```




TESTING REGRESSION TABLES
```{r, results = "hide"}
stargazer(lm_sep1, type = "text", title="Linear Model - FULL ", digits=1, out="Regression_Tables_Using_Score_04.12.16.txt")

stargazer(lm_cover_crop, lm_crop_rotation, lm_manure, lm_direct_planting, lm_production_diversity, lm_apm, type = "text", title="Linear Model - FULL ", digits=1, out="Regression_Tables_Individ_Indep_04.12.16.txt")

stargazer(lm_agrichemcials, type = "text", title="Linear Model - FULL ", digits=1, out="Regression_Tables_Agrichem_04.12.16.txt")
```


Similar results as before: credit_access still the biggest predictor. 

MAPS! 
link to blog using brazilian municipalities shapefile 
https://dioferrari.wordpress.com/2014/11/27/plotting-maps-using-r-example-with-brazilian-municipal-level-data/



