---
title: "Stepwise"
author: "Jill Guerra"
date: "April 19, 2016"
output: 
  html_document:
    keep_md: true
---
###PART 1: LOAD DATA, CREATE SCALE
***
This section loads the packages, imports data and cleans the data of small farms and observations with NA values 
####PACKAGES
```{r packages }
library(ggplot2)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gridExtra)) # for grid.arrange 
suppressPackageStartupMessages(library("moments")) # for skew & kurtosis
suppressPackageStartupMessages(library(knitr)) # for nice tables 
suppressPackageStartupMessages(library(ggbiplot)) # for PCA analysis 
suppressPackageStartupMessages(library(devtools)) # for PCA analysis as well, I believe 
suppressPackageStartupMessages(library(psych)) # needed for chronbach's alpha
suppressPackageStartupMessages(library(stats)) 
suppressPackageStartupMessages(library(stargazer)) 
```

#### DATA SET UP  - This should be in every file that I am working on)
```{r load data set}
rawdf_aei<- read.csv("~/AEI_Index/Census_data_formatted_for_R_04.12.16.csv", quote = '"', sep = ",", na.strings = c(".",""), strip.white = TRUE) # load full dataset
# note that this dataset was updated in a feb 22 version to only have variables that I will be working with 
```

```{r drop observations with <50 farms, results = 'hide'}

small <- c("4202453", "4202008", "4208450", "4202057", "4201950", "4206306") # these are the codes for the municipalities that have fewer than 50 farms. Names in Result_tracking Rmd. 

'%!in%' <- function(x,y)!('%in%'(x,y)) # sweet function for negating an %in% function 

# drop the municipalities that are held in the 'small' value. 
df_aei <- rawdf_aei %>% 
  filter(code %!in% small) %>% 
  droplevels()  # need to drop levels or else the new data.frame will continue to store the other factors even though they aren't being used. See Homework 5 from stats class for more about this. 

str(df_aei) # check the factor levels. It should match the #obs shown in the global environment section. If it does not then the droplevels() didn't work. 

```

```{r drop observations with NAs}
na_obs <- df_aei[rowSums(is.na(df_aei)) > 0,] # pulls out new data.frame with just the NA values

na_obs_names <- na_obs[,1]

df_aei <- df_aei %>% 
  filter(code %!in% na_obs_names) %>% 
  droplevels()

nlevels(df_aei$municipality) # should be 273! 

```

###PART 2: SCALE CREATION 
***
This section will define the Agscores scale and bind it to the original dataframe, but stored in a new dataframe ('df_aei_score')

####SCALE  
```{r}
#columns from current dataset:

# current column numbers for orgcomp (3), manure (4), cover_crop (5), crop_rotationation (6), apm(7), production diversity (8) direct_planting(9)
ae_scale_old <- df_aei[,c(4:9)] # this one looks the best. It excludes organic compost because it as negatively related in the alpha of the scale in which it was included 
alpha(ae_scale_old)
# chronbach's is 0.73

# new scae that looks pretty good. 
ae_scale <- df_aei[,c(5:9)] 
alpha(ae_scale) #= 0.74

cor(df_aei$direct_planting, df_aei$credit_access)

```

```{r create the index and bind, results='hide'}
#Creating scores
agscores <- ((df_aei$apm +df_aei$crop_rotation + df_aei$direct_planting + df_aei$manure + df_aei$cover_crop + df_aei$production_diversity)/6) # testing one score set 

str(agscores)

# bind the scores onto the original dataframe but store as a new dataframe
df_aei_scores <- cbind(df_aei, agscores) 
df_aei_scores
write.csv(df_aei_scores, file = "df_aei_scores.csv")
```

###STEPWISE BASED ON INITIAL RESULTS 
```{r stepwise results }
lm_res_1 <- lm(agscores ~ credit_access, df_aei_scores)
lm_res_2 <- lm(agscores ~ credit_access + only_family_labour, df_aei_scores)
lm_res_3 <- lm(agscores ~ credit_access + only_family_labour + off_farm_income, df_aei_scores)
lm_res_4 <- lm(agscores ~ credit_access + only_family_labour + off_farm_income + extension, df_aei_scores)
lm_res_5 <- lm(agscores ~ credit_access + only_family_labour + off_farm_income + extension + low_income, df_aei_scores)
lm_res_6 <- lm(agscores ~ credit_access + only_family_labour + off_farm_income + extension + low_income + farmers_association, df_aei_scores)

stargazer(lm_res_1, lm_res_2, lm_res_3, lm_res_4,lm_res_5,lm_res_6, type = "text", title="Linear Model - FULL ", digits=1, out="Stepwise_results_04.19.16.txt")

```

###STEPWISE BASED ON LITERATURE
```{r stepwise results }
lm_lit_1 <- lm(agscores ~ extension, df_aei_scores)
lm_lit_2 <- lm(agscores ~ extension + farmers_association, df_aei_scores)
lm_lit_3 <- lm(agscores ~ extension + farmers_association + credit_access, df_aei_scores)
lm_lit_4 <- lm(agscores ~ extension + farmers_association + credit_access + only_family_labour, df_aei_scores)
lm_lit_5 <- lm(agscores ~ extension + farmers_association + credit_access + only_family_labour + off_farm_income, df_aei_scores)
lm_lit_6 <- lm(agscores ~ extension + farmers_association + credit_access + only_family_labour + off_farm_income +  low_income, df_aei_scores)

stargazer(lm_lit_1, lm_lit_2, lm_lit_3, lm_lit_4,lm_lit_5,lm_lit_6, type = "text", title="Linear Model - FULL ", digits=1, out="Stepwise_literature_04.19.16.txt")

```

```{r Stepwise based on results }
lm_res2_1 <- lm(agscores ~ credit_access, df_aei_scores)
lm_res2_2 <- lm(agscores ~ credit_access + low_income, df_aei_scores)
lm_res2_3 <- lm(agscores ~ credit_access + low_income + only_family_labour, df_aei_scores)
lm_res2_4 <- lm(agscores ~ credit_access + low_income + only_family_labour + off_farm_income + extension, df_aei_scores)
lm_res2_5 <- lm(agscores ~ credit_access + low_income + only_family_labour + off_farm_income + extension, df_aei_scores)
lm_res2_6 <- lm(agscores ~ credit_access + low_income + only_family_labour + off_farm_income + extension + low_income + farmers_association, df_aei_scores)

stargazer(lm_res2_1, lm_res2_2, lm_res2_3, lm_res2_4,lm_res2_5,lm_res2_6, type = "text", title="Stepwise Regression", digits=1, dep.var.labels=c("Aggregate score", "Aggregate score", "Aggregate score", "Aggregate score", "Aggregate score", "Aggregate score"), covariate.labels = c("Low income", "Credit access", "Extension",  "Farmers' association", "Only family labour", "Off farm income"), out="Stepwise_results_05.10.16.txt")

```

